Model LF

### 2022-09-20 max_dp endogen stød.Rmd
commit

@@

@@

  alpha_143 = TIMESERIES(c(alpha_143),   
                        START=c(2005,2),FREQ=4),
   mean_yd2a_hk = TIMESERIES(c(mean_yd2a_hk),   
                       START=c(2005,2),FREQ=4),

>>>>

alpha_200 =reg_15$coefficients[1]
alpha_200=ts(alpha_200,start = c(2005,2), end = c(2020,1), frequency = 4 )

alpha_201=reg_15$coefficients[2]
alpha_201=ts(alpha_201,start = c(2005,2), end = c(2020,1), frequency = 4 )

alpha_202=reg_15$coefficients[3]
alpha_202=ts(alpha_202,start = c(2005,2), end = c(2020,1), frequency = 4 )

alpha_203=reg_15$coefficients[4]
alpha_203=ts(alpha_203,start = c(2005,2), end = c(2020,1), frequency = 4 )

mean_pm= mean(pm)
mean_pm=ts(mean_pm,start = c(2005,2), end = c(2020,1), frequency = 4)

@@

COMMENT> 
IDENTITY> pm
EQ> pm = pm_ds + alpha_200 + alpha_201*SD1 + alpha_202*SD2 + alpha_203*SD3 - mean_pm

@@

  alpha_143 = TIMESERIES(c(alpha_143),   
                        START=c(2005,2),FREQ=4),
   mean_yd2a_hk = TIMESERIES(c(mean_yd2a_hk),   
                       START=c(2005,2),FREQ=4),
  alpha_200 = TIMESERIES(c(alpha_200),   
                        START=c(2005,2),FREQ=4),

  alpha_201 = TIMESERIES(c(alpha_201),   
                        START=c(2005,2),FREQ=4),

  alpha_202 = TIMESERIES(c(alpha_202),   
                        START=c(2005,2),FREQ=4),

  alpha_203 = TIMESERIES(c(alpha_203),   
                        START=c(2005,2),FREQ=4),
   mean_pm = TIMESERIES(c(mean_pm),   
                       START=c(2005,2),FREQ=4),
